Type theory in type theory using single substitutions

### 2024-03-07 types_2024/abstract.tex
finalise abstract

We formalised the single substitution calculus with an infinite
hierarchy of types closed under $\Pi$ and $\U$ as a quotient
inductive-inductive type in Agda, proved $\alpha$-normalisation for
it, and derived all the rules for the parallel substitution calculus
(CwF equipped with $\Pi$ types and $\U$).

>>>>

We formalised single substitution calculus with an infinite hierarchy
of types closed under $\Pi$ and $\U$ as a quotient inductive-inductive
type in Agda, proved $\alpha$-normalisation, and derived all the rules
for parallel substitutions (CwF equipped with $\Pi$ types and $\U$):
\url{https://bitbucket.org/akaposi/single}.
